Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-26 analysis/paper/paper.Rmd
Add new figures
Add figures for all statistical analyses performed

In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher. The AWD water management, which was lower than the FLD treatment, was also significantly different.

@@

In 2016 the neither of the treatments, nitrogen rate or water management, were significantly different from the control treatments for leaf ShB severity.

@@

@@

@@

```{r TShB-sev, fig.cap="Tiller sheath blight severity progress was measured in the 2016 experiment at four assessment points. Sheath blight severity was rated on an unevenly spaced ordinal scale and converted to the mid-point percentage value to calculate the area under the disease progress stairs (AUDPS). Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
ggplot(subset(AUDPS, YEAR == 2016),
       aes(x = WMGT, y = TShB_percent_AUDPS)) +
  geom_boxplot() +
  geom_point() +
  xlab("Treatment") +
  ylab("AUDPS") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"))
```

```{r TShB-inc, fig.cap="Tiller sheath blight incidence per hill in the 2015 and 2016 experiments. Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD). Sheath blight incidence was calculated as the number of tillers per hill that were infected with sheath blight divided by the whole number of tillers in the hill. Differing inoculation techniques were used in the 2015 and 2016 experiments, leading to a higher rate of incidence in 2016."}
ggplot(RAW_data, aes(x = WMGT, y = TShB_incidence)) +
  geom_boxplot(fill = NA) +
  theme(axis.text.x = element_text(size = 8,
                                   angle = 45,
                                   hjust = 1)) +
  xlab("Treatment") +
  ylab("Incidence per Hill") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  facet_grid(. ~ YEAR)
```

>>>>

In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher (Figure \@ref(fig:TShB-N-sev)). The AWD water management, which was lower than the FLD treatment, was also significantly different (Figure \@ref(fig:TShB-W-sev)).

@@

In 2016 the neither of the treatments, nitrogen rate or water management, were significantly different from the control treatments for leaf ShB severity (Figures \@ref(fig:LShB-W-sev), \@ref(fig:LShB-N-sev)).

@@

##### Tiller ShB progress

@@

##### Leaf ShB progress

@@

##### Tiller ShB incidence - WMGT

```{r TShB-W-inc, fig.cap="Tiller sheath blight incidence progress was measured in the 2015 at five assessment points and 2016 experiment at four points. Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS). Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
ggplot(AUDPS,
       aes(x = WMGT, y = TShB_inc_AUDPS)) +
  geom_boxplot() +
  geom_point() +
  xlab("Treatment") +
  ylab("AUDPS") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  facet_grid(. ~ YEAR,
             scales = "free_x")
```

##### Tiller ShB incidence - NRTE

```{r TShB-N-inc, fig.cap="Tiller sheath blight incidence progress was measured in the 2015 at five assessment points and 2016 experiment at four points. Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS). Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120). In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}
ggplot(AUDPS,
       aes(x = NRTE, y = TShB_inc_AUDPS)) +
  geom_boxplot() +
  geom_point() +
  xlab("Treatment") +
  ylab("AUDPS") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  facet_grid(. ~ YEAR,
             scales = "free_x")
```

##### Tiller ShB severity - WMGT

```{r TShB-W-sev, fig.cap="Tiller sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points. Sheath blight severity was rated on an unevenly spaced ordinal scale and converted to the mid-point percentage value to calculate the area under the disease progress stairs (AUDPS). Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
ggplot(AUDPS,
       aes(x = WMGT, y = TShB_sev_AUDPS)) +
  geom_boxplot() +
  geom_point() +
  xlab("Treatment") +
  ylab("AUDPS") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  facet_grid(. ~ YEAR,
             scales = "free_x")
```

##### Tiller ShB severity - NRTE

```{r TShB-N-sev, fig.cap="Tiller sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points. Sheath blight severity was rated on an unevenly spaced ordinal scale and converted to the mid-point percentage value to calculate the area under the disease progress stairs (AUDPS). Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120). In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}
ggplot(AUDPS,
       aes(x = NRTE, y = TShB_sev_AUDPS)) +
  geom_boxplot() +
  geom_point() +
  xlab("Treatment") +
  ylab("AUDPS") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  facet_grid(. ~ YEAR,
             scales = "free_x")
```

##### Leaf ShB severity - WMGT

```{r LShB-W-sev, fig.cap="Leaf sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points. Sheath blight severity was rated on an unevenly spaced ordinal scale and converted to the mid-point percentage value to calculate the area under the disease progress stairs (AUDPS). Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
ggplot(AUDPS,
       aes(x = WMGT, y = LShB_percent_AUDPS)) +
  geom_boxplot() +
  geom_point() +
  xlab("Treatment") +
  ylab("AUDPS") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  facet_grid(. ~ YEAR,
             scales = "free_x")
```

##### Leaf ShB severity - NRTE

```{r LShB-N-sev, fig.cap="Leaf sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points. Sheath blight severity was rated on an unevenly spaced ordinal scale and converted to the mid-point percentage value to calculate the area under the disease progress stairs (AUDPS). Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120). In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}
ggplot(AUDPS,
       aes(x = NRTE, y = LShB_percent_AUDPS)) +
  geom_boxplot() +
  geom_point() +
  xlab("Treatment") +
  ylab("AUDPS") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  facet_grid(. ~ YEAR,
             scales = "free_x")
```
